---
output:
    pdf_document:
        includes:
            in_header: import.sty
---

\begin{figure}
\begin{center}
  \captionsetup{labelformat=empty}
  \caption{\textbf{Figure S1:} Expression of dentate granule cell markers discovered in the study in Allen Brain Atlas mouse brain in situ hybridization database.}
  \includegraphics[height = 10in]{DentateGranule_singlePages/01.png}
  \label{fig:allenAllDentate}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
  \includegraphics[height = 10in]{DentateGranule_singlePages/05.png}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
  \includegraphics[height = 10in]{DentateGranule_singlePages/09.png}
\end{center}
\end{figure}


\begin{figure}
\begin{center}
  \includegraphics[height = 10in]{DentateGranule_singlePages/13.png}
\end{center}
\end{figure}


\begin{figure}
\begin{center}
  \includegraphics[height = 10in]{DentateGranule_singlePages/17.png}
\end{center}
\end{figure}



\begin{figure}
\begin{center}
  \includegraphics[height = 10in]{DentateGranule_singlePages/21.png}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
  \includegraphics[height = 7.5in]{DentateGranule_singlePages/25.png}
\end{center}
\end{figure}

\newpage



\begin{figure}
\begin{center}
  \captionsetup{labelformat=empty}
  \caption{\textbf{Figure S2:} Expression of purkinje markers discovered in the study in Allen Brain Atlas mouse brain in situ hybridization database.}
  \includegraphics[height = 10in]{Purkinje_singlePages/01.png}
  \label{fig:allenAllPurkinje}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
  \includegraphics[height = 10in]{Purkinje_singlePages/05.png}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
  \includegraphics[height = 10in]{Purkinje_singlePages/09.png}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
  \includegraphics[height = 10in]{Purkinje_singlePages/13.png}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
  \includegraphics[height = 10in]{Purkinje_singlePages/17.png}
\end{center}
\end{figure}


\begin{figure}
\begin{center}
  \includegraphics[height = 10in]{Purkinje_singlePages/21.png}
\end{center}
\end{figure}


\begin{figure}
\begin{center}
  \includegraphics[height = 10in]{Purkinje_singlePages/25.png}
\end{center}
\end{figure}


\begin{figure}
\begin{center}
  \includegraphics[height = 10in]{Purkinje_singlePages/29.png}
\end{center}
\end{figure}


\begin{figure}
\begin{center}
  \includegraphics[height = 10in]{Purkinje_singlePages/33.png}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
  \includegraphics[height = 10in]{Purkinje_singlePages/37.png}
\end{center}
\end{figure}

\begin{figure}
<<<<<<< HEAD

\textbf{Table S1:} Validation status of dentate granule cell markers.

```{r,echo=FALSE}
granule = ogbox::read.design('DentateGranule.tsv')
knitr::kable(granule,format= 'latex')
```
\end{figure}


\begin{figure}

\textbf{Table S2:} Validation status of purkinje cell markers.

```{r,echo=FALSE}
purkinjeTable = ogbox::read.design('Purkinje.tsv')
knitr::kable(purkinjeTable,format= 'latex')
```

\end{figure}


```{r,include=FALSE}
library(magrittr)
library(ogbox)
library(ggplot2)
library(cowplot)
Pter = ogbox::read.design('Pter hipposeq.tsv')
St8sia4 = ogbox::read.design('St8sia4 hipposeq.tsv')

frame = rbind(Pter,St8sia4) %>% 
    dplyr::mutate(CellType = replaceElement(sample_name,c('ca1_d' = 'CA1 Dorsal',
                                                          'ca1_v' ='CA1 Ventral',
                                                          'ca2' = 'CA2',
                                                          'ca3_d' = 'CA3 Dorsal',
                                                          'ca3_v' = 'CA3 Ventral',
                                                          'mc' = 'Mossy cell',
                                                          'dg_d' = 'Dentate Granule Dorsal',
                                                          'dg_v' = 'Dentate Granule Ventral'))$newVector)

frame$CellType =  factor(frame$CellType,levels = c('Dentate Granule Dorsal',
                                                     'Dentate Granule Ventral',
                                                     trimElement(unique(frame$CellType),
                                                     c('Dentate Granule Dorsal',
                                                     'Dentate Granule Ventral'))))

(frame %>% ggplot(aes(x = CellType,y = fpkm, ymin = conf_lo, ymax = conf_hi)) + geom_errorbar() + geom_point() +  facet_wrap(~gene_short_name,scales = 'free') + xlab('') +theme(axis.text.x  =element_text(angle=90))) %>% 
    ggsave(filename = 'hippposeqSup.png',device = 'png',height = 4,width = 4)

```

\begin{figure}
\begin{center}
  \captionsetup{labelformat=empty}
  \caption{\textbf{Figure S3:} Expression of Pter and St8sia4 in pooled RNA-seq data from Hipposeq. Data acquired from http://hipposeq.janelia.org}
  \includegraphics[height = 4in]{hippposeqSup.png}
=======
\begin{center}
  \includegraphics[height = 2.5in]{Purkinje_singlePages/41.png}
>>>>>>> 25c2c8996759397e4709916bdd0f256e96986573
\end{center}
\end{figure}
