---
output:
    pdf_document:
        includes:
            in_header: import.sty
---

\begin{figure}
\begin{center}
  \captionsetup{labelformat=empty}
  \caption{\textbf{Figure S1:} Expression of dentate granule cell markers discovered in the study in Allen Brain Atlas mouse brain in situ hybridization database.}
  \includegraphics[height = 10in]{DentateGranule_singlePages/01.png}
  \label{fig:allenAllDentate}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
  \includegraphics[height = 10in]{DentateGranule_singlePages/05.png}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
  \includegraphics[height = 10in]{DentateGranule_singlePages/09.png}
\end{center}
\end{figure}


\begin{figure}
\begin{center}
  \includegraphics[height = 10in]{DentateGranule_singlePages/13.png}
\end{center}
\end{figure}


\begin{figure}
\begin{center}
  \includegraphics[height = 10in]{DentateGranule_singlePages/17.png}
\end{center}
\end{figure}



\begin{figure}
\begin{center}
  \includegraphics[height = 10in]{DentateGranule_singlePages/21.png}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
  \includegraphics[height = 7.5in]{DentateGranule_singlePages/25.png}
\end{center}
\end{figure}

\newpage



\begin{figure}
\begin{center}
  \captionsetup{labelformat=empty}
  \caption{\textbf{Figure S2:} Expression of purkinje markers discovered in the study in Allen Brain Atlas mouse brain in situ hybridization database.}
  \includegraphics[height = 10in]{Purkinje_singlePages/01.png}
  \label{fig:allenAllPurkinje}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
  \includegraphics[height = 10in]{Purkinje_singlePages/05.png}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
  \includegraphics[height = 10in]{Purkinje_singlePages/09.png}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
  \includegraphics[height = 10in]{Purkinje_singlePages/13.png}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
  \includegraphics[height = 10in]{Purkinje_singlePages/17.png}
\end{center}
\end{figure}


\begin{figure}
\begin{center}
  \includegraphics[height = 10in]{Purkinje_singlePages/21.png}
\end{center}
\end{figure}


\begin{figure}
\begin{center}
  \includegraphics[height = 10in]{Purkinje_singlePages/25.png}
\end{center}
\end{figure}


\begin{figure}
\begin{center}
  \includegraphics[height = 10in]{Purkinje_singlePages/29.png}
\end{center}
\end{figure}


\begin{figure}
\begin{center}
  \includegraphics[height = 10in]{Purkinje_singlePages/33.png}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
  \includegraphics[height = 10in]{Purkinje_singlePages/37.png}
\end{center}
\end{figure}

\begin{figure}

\textbf{Table S1:} Validation status of dentate granule cell markers.

```{r,echo=FALSE}
granule = ogbox::read.design('DentateGranule.tsv')
knitr::kable(granule,format= 'latex')
```
\end{figure}


\begin{figure}

\textbf{Table S2:} Validation status of purkinje cell markers.

```{r,echo=FALSE}
purkinjeTable = ogbox::read.design('Purkinje.tsv')
knitr::kable(purkinjeTable,format= 'latex')
```

\end{figure}
